PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-12 paper/sec-results.tex
Provisional results for Z pT

\paragraph{Experimental measurements and process features.}
We select the single-differential transverse momentum distribution of the
the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a centre-of-mass
energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. While this measurement is not
included in any PDF determination, its expected impact on parton densities has been studied in 
ref.~\cite{Boughezal:2017nla}. Since this process shows very low experimental uncertainties (at the percent level or below), and is
known to an excellent degree as far as QCD corrections are concerned~\cite{Gehrmann-DeRidder:2017mvr,Bizon:2019zgf} {\bf MZ there are at least 5-6 other papers both
by the zurich group and the argonne one, but on Z+jet rather than z-pt predictions. Should we cite them?}
EW corrections are expected to be essential in order to achieve a good
description of it, and to constrain accurately the PDFs. Analogous measurements,
from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt}, were partly included (upon
selection of an appropriate kinematic cut that excluded bins with large EW
corrections) in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
single LO contribution $\mathcal{O}(\alphas\alpha^2)$ and a single NLO
contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
we supplement these with another LO and NLO, which are
$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alphas\alpha^3)$;
contributions of the order $\mathcal{O}(\alpha^4)$ are not considered (see ref.~\cite{Denner:2019zfp}).
EW corrections for this process were computed in
refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
The process receives contributions from 101 (166) parton luminosities,
see appendix~\ref{app:lumis} for details.

@@

As in the case of Drell-Yan, we use a fixed value for the renormalisation and factorisation 
scales $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$.
We require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$, $|\eta_\ell|<2.4$,
$|M_{\ell\bar\ell} - M_\mathrm{Z}| < \SI{15}{\giga\electronvolt}$,
$|y_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_\mathrm{T}^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
transverse momentum and pseudorapidity of each lepton, and for the invariant mass,
pseudorapidity and transverse momentum of the lepton pair. Imposing a minimum cut for the transverse momentum of the lepton pair 
is necessary as we rely on a fixed-order computation, without including resummation effects.

\paragraph{Numerical results.} We finally

@@

>>>>

\paragraph{Experimental measurements and process features.}
We select the single-differential transverse momentum distribution of the
the Z boson, $p_\mathrm{T}^\mathrm{Z}$, measured by the CMS experiment at a centre-of-mass
energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}. While this measurement is not
included in any PDF determination, its expected impact on parton densities has been studied in 
ref.~\cite{Boughezal:2017nla}. Since this process shows very low experimental uncertainties (at the percent level or below), and is
known to an excellent degree as far as QCD corrections are concerned~\cite{Gehrmann-DeRidder:2017mvr,Bizon:2019zgf} {\bf MZ there are at least 5-6 other papers both
by the zurich group and the argonne one, but on Z+jet rather than z-pt predictions. Should we cite them?}
EW corrections are expected to be essential in order to achieve a good
description of it, and to constrain accurately the PDFs. Analogous measurements,
from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt}, were partly included (upon
selection of an appropriate kinematic cut that excluded bins with large EW
corrections) in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
single LO contribution $\mathcal{O}(\alphas\alpha^2)$ and a single NLO
contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
we supplement these with another LO and NLO, which are
$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alphas\alpha^3)$;
contributions of the order $\mathcal{O}(\alpha^4)$ are not considered (see ref.~\cite{Denner:2019zfp}).
EW corrections for this process were computed in
refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum}.
The process receives contributions from 101 (166) parton luminosities,
see appendix~\ref{app:lumis}.

@@

As in the case of Drell-Yan, we use a fixed value for the renormalisation and
factorisation scales $\mu_\mathrm{R}=\mu_\mathrm{F}=M_\mathrm{Z}$, where
$M_\mathrm{Z}$ is the $\mathrm{Z}$-boson mass. Consistently with the
experimental analysis, we require $p_\mathrm{T}^\ell>\SI{25}{\giga\electronvolt}$,
$|\eta_\ell|<2.4$, $|M_{\ell\bar\ell} - M_\mathrm{Z}| < \SI{15}{\giga\electronvolt}$,
$|y_{\ell\bar\ell}|<2.4$ and $\SI{20}{\giga\electronvolt}<p_\mathrm{T}^{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$ for the
transverse momentum and pseudorapidity of each lepton, and for the invariant
mass, pseudorapidity and transverse momentum of the lepton pair.
We finally discard all bins with
$p_\mathrm{T}^\mathrm{Z}<\SI{20}{\giga\electronvolt}$ to avoid a kinematic
ergion where resummation effects are sizeable.

\paragraph{Numerical results.} In figure~\ref{fig:cmsZ13TeV} we report the
distribution differential in the transverse momentum of the $\mathrm{Z}$
boson. Also in this case, the \textsc{PineAPPL} result is well validated, as it
differs from the MC result by $\SI{0.5}{\permille}$ at most. The accuracy of the
theory or the choice of scale do not alter this conclusion.

@@

The process receives its leading contribution from $\mathrm{qg}$ and
$\bar{\mathrm{q}}g$ initiated channels, which account for about 65\%
of the cross section, with some variations in the relative contributions from
individual quark and atiquark flavours as the transverse momentum of the
$\mathrm{Z}$ boson varies; the PI contribution always remain negligible.
Overall, the EW corrections suppress the theoretical predictions by about
2\% -- 7\% as the transverse momentum of the $\mathrm{Z}$ boson increases.
The size of this shift is usually as large as the data uncertainty, and
exceeds it at large values of $p_\mathrm{T}^\mathrm{Z}$. As a consequence,
we anticipate the inclusion of EW corrections to be relevant for an accurate
fit to this data set.

The size of the EW correction is between four and six times larger than the
size of the PDF uncertainty: as previously noted in th eother cases, this fact
suggests that, once included in a PDF fit, EW corrections can improve the
accuracy of the PDFs. In comparison to the scale ucnertainty, the size of the
EW corrections remains negligible, as NNLO QCD corrections are comparatively
large, as expected in a process mostly initiated by gluons. They should
therefore be included along with EW corrections in a fit of PDFs. Finally, the
Monte Carlo uncertainty is well under control, as it remains mostly negligible
in comparison to the PDF, scale and data uncertainty.
